---
title: "IRR Calculator"
author: "Michael Bristow"
date: "18 December 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##  IRR Calculator - Developing Data Products - Week 4 Project

This shiny project shows a comparison between calculated IRR and interpolated IRR

It is used to graphically show the difference between the two figures.

By adjusting the two discount factors used to be as close to the IRR, the two figures will converge


## Usage

- Default values for the cashflows for a 5 year project are laoded
- Calculated IRR is displayed
- Graph shows the interpolated IRR as well as the calculate IRR for comparison

- The app is hosted at https://mickyb.shinyapps.io/IRRCalc2/
- Source coded is at https://github.com/mickbristow/IRRCalc
- RPubs documentation is at http://rpubs.com/mickbristow/342869

## Code snippets

```{r echo=FALSE, message=FALSE, results='asis', warning = FALSE}
library(FinancialMath)
library(plotly)
```

Snippet of the ui Code
```{r eval=FALSE, echo=TRUE}
 mainPanel(
      h3("Calculated IRR"),
      textOutput("calc_IRR"),
      h3("Initial NPV"),
      textOutput("calc_NPV1"),
      h3("Second NPV"),
      textOutput("calc_NPV2"),
      #h3("IRR via extrapolation"),
      plotlyOutput("extrapolatelot")
```
## Output plot

```{r echo=FALSE, message=FALSE, warning = FALSE}
cflows <- c(100,200,300,400,500)


irr <- IRR(cf0=-1000,cf=c(100,200,300,400,500),times=c(1,2,3,4,5))

df1 <- .10
npv1 <- NPV(cf0=-1000,cf=c(100,200,300,400,500),times=c(1,2,3,4,5),df1)


df2 <- .15
npv2 <- NPV(cf0=-1000,cf=c(100,200,300,400,500),times=c(1,2,3,4,5),df2)


library(plotly)
df1 <- (df1 * 100)
df2 <- (df2 * 100)
#df <- data.frame(x,y)
df <- data.frame(c(df1,df2),c(npv1,npv2))


colnames(df) <- c("x","y")

irr <- (irr *100)

a <- list(
  x = irr,
  y = 0,
  text = "Calculated IRR",
  xref = "x",
  yref = "y",
  showarrow = TRUE,
  arrowhead = 7,
  ax = 40,
  ay = -40
)


p <- plot_ly(df, x = ~x, y = ~y, type = 'scatter', mode = 'lines')  %>% 
#  layout(title="IRR Calculation", xaxis=list(title="Discount Factor", range = c(0, 20)),
  layout(title="IRR Calculation", xaxis=list(title="Discount Factor"), 
         yaxis=list(title="NPV (+/-)"), annotations = a)

p
```

